Lens Modeling in \sw

### 2014-01-12 text/ms.tex
Test

Our present picture of the formation of the largest structures in the
Universe --- galaxies and clusters of galaxies --- is that
gravitational instabilities (whose early stages are observable as
fluctuations of the microwave background) caused a collapse into
gravitationally bound structures.  Dark matter would have dominated
the initial collapse, but once deep wells in the gravitational
potential appeared, gas would have fallen into them while radiating
away its gravitational potential energy through atomic processes to
form the first stars and galaxies.  With time, galaxies and clusters
would continue to merge and change their form.  This rough outline is
well-established now, but many puzzles remain to be solved before our
understanding is satisfactory.  To progress towards solving these, we
need more knowledge of dark matter.  And to study dark matter,
gravitational lensing is attractive, because it depends only on mass.

>>>>

xxx
Our present picture of the formation of the largest structures in the
Universe --- galaxies and clusters of galaxies --- is that
gravitational instabilities (whose early stages are observable as
fluctuations of the microwave background) caused a collapse into
gravitationally bound structures.  Dark matter would have dominated
the initial collapse, but once deep wells in the gravitational
potential appeared, gas would have fallen into them while radiating
away its gravitational potential energy through atomic processes to
form the first stars and galaxies.  With time, galaxies and clusters
would continue to merge and change their form.  This rough outline is
well-established now, but many puzzles remain to be solved before our
understanding is satisfactory.  To progress towards solving these, we
need more knowledge of dark matter.  And to study dark matter,
gravitational lensing is attractive, because it depends only on mass.
